The unequal distribution of access to education and transport: insights from the São Paulo Metropolitan Region

### 2017-02-26 paper.tex
Reword data section

z school accessibility index, we use data from three
different sources. The first one is the 2008 School Census of the
Brazilian National Institute of Educational Studies and Surveys (INEP),
which provides information on the (universe) of public educational
institutions, including a unique identifier and the number of students
enrolled in secondary education. We use the coordinates contained in the
database provided by the Center for Metropolitan Studies CEM
(\textit{Centro de Estudos da Metrópole}) for 2001 to geolocate the
schools in 2008 using the unique identifier. In order to include new
schools built between 2001 and 2008, we used a dataset provided by the
Fundação SEADE (São Paulo State Agency for Statistical Analysis)
containing the goecoded location for all state administration schools at
2008. The final dataset set was obtained merging this two data source
using the standard ID used by the INEP. We geo-localized a total of
4,612 public schools in the SPRM.

Our second source is information the 2010 Population Census of Brazil,
compiled and freely distributed by the Brazilian Institute of Statistics
(IBGE). We aggregate the data by Area de Ponderacão Espacial (AEP)
areas, a spatial unit defined for surveying purposes by IBGE. There is a
total of 633 areas in the SPMR. IBGE provides the digital networks
containing the boundaries of these areas. From the census microdata, we
have data on the number of inhabitants by age for each enumeration area.
The number of adolescents in secondary school age (ages 15-18) is
1'216.611 (approximately 13 percent of the population).

>>>>

The school accessibility index was created using data from three main
sources: a 2008 School Census; school location data; and geographical
route data generated by the Google Matrix API.

The School Census data was provided by the
Brazilian National Institute of Educational Studies and Surveys (INEP).
The dataset contains information on all public educational
institutions, including a unique identifier and the number of students
enrolled in secondary education. School coordinates contained in a
database provided by the Center for Metropolitan Studies CEM
(\textit{Centro de Estudos da Metrópole}) for 2001 were used to
geolocate the schools in 2008 using the unique identifier.
To include new
schools built between 2001 and 2008, we used a dataset provided by the
Fundação SEADE (São Paulo State Agency for Statistical Analysis)
containing the goecoded location for all state administration schools at
2008. The this dataset set was obtained merging this two data source
using the standard ID used by the INEP. We geo-localized a total of
4,612 public schools in the SPRM.

The second source was the 2010 Population Census of Brazil,
compiled and freely distributed by the Brazilian Institute of Statistics
(IBGE). We aggregated the data by 633 administrative zones in the
SPMR: Area de Ponderacão Espacial (AEP)
areas, a spatial unit defined for surveying purposes by IBGE.
IBGE provides geographical datasets
containing the boundaries of these areas. From the census microdata, we
have data on the number of inhabitants by age for each enumeration area,
which totals more than one million secondary school students:
1,216,611 people of secondary school age (15 - 18 years) were recorded
in the Census dataset (approximately 13 percent of the population).
